\documentclass[12pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}  % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\input macros.tex

\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

\pagestyle{fancy} % allows you to use the header and footer commands


\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.


\pagestyle{fancy} \lhead{\doctitle} \rhead{S.M. Couch} \renewcommand{%
\headrulewidth}{0.0pt}

\begin{center}
\bf \large {REQUEST FOR INFORMATION} \\
\end{center}

\vspace{-.25in}

Data management for this project will be accomplished primarily with the open-source Python-based simulation management and provenance tool we are developing.
Simulation metadata, and the full 3D progenitor structures we will generate, will be shared through servers available to PI Couch at MSU.

\vspace{-.15in}
\begin{itemize}

\item Does your community currently share data? If yes, what
  mechanisms are employed? \\
No.  Simulation data is not typically shared in our community.\\
\item What is the effective lifetime of useful data from your
  community? Do data storage requirements entail preserving data for
  weeks? Months? Years? \\
Years.  Simulation data can be mined for useful insight well into the future.\\
\item Characterize short- and long-term data storage requirements for
  you and/or your community.\\
Typically short-term storage (on-disk) would be desired for up to a
year, or until after all papers hinging on analysis of the data are
accepted for publication.  \\
\item What types of tools for data storage, compression (reduction),
  movement, and analysis do you currently use? Where do you see the
  need for tools development?\\
HDF5, Globus Online.
\end{itemize}
\vspace{-.15in}


\end{document}
